---
title: "Analysis"
output:  
  html_document:
    number_sections: true
    toc: true  
    collapsed: false
    toc_float: true
    smooth_scroll: false
    toc_depth: 3
    self_contained: yes
---

```{r, message = FALSE, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
# packages
library(ez)
library(ggplot2)
library(plyr)
library(pastecs)
library(ez)
library(data.table)
library(overlapping) # to compute the 
library(tidyr)
library(showtext)
#install.packages("expss")
library(expss)
library(dplyr)

font_add_google("Poppins", "Poppins")
font_add_google("Roboto Mono", "Roboto Mono")
showtext_auto()
```





```{r}
# read data 
library(readr)
tdata <- read_csv("tdata_final.csv")
```
# Demographics

```{r}
table(tdata$gender) #%>% sum()

#tdata$age <- as.numeric(tdata$age)

mean(tdata$age)
sd(tdata$age)
min(tdata$age)
max(tdata$age)
```
# Data handling

```{r}

# add a column that represents the transformations as a factor
tdata$Transformation <- factor(tdata$test_stimulus, 
                               levels = c("img/Left_Y_Symmetry_Big.svg",
                                          "img/Left_Y_Symmetry_Angle.svg",
                                          "img/Left_Y_Symmetry_X_Rotation.svg",
                                          "img/Left_Y_Symmetry_X_Rotation_180.svg",
                                          "img/Left_Y_Symmetry_X_Symmetry.svg",
                                          "img/Left_Y_Symmetry_Y_Translation.svg",
                                          "img/Left_Y_Symmetry_X_Translation.svg",
                                          "img/Right_Y_Symmetry_Big.svg",
                                          "img/Right_Y_Symmetry_Angle.svg",
                                          "img/Right_Y_Symmetry_X_Rotation.svg",
                                          "img/Right_Y_Symmetry_X_Rotation_180.svg",
                                          "img/Right_Y_Symmetry_X_Symmetry.svg",
                                          "img/Right_Y_Symmetry_Y_Translation.svg",
                                          "img/Right_Y_Symmetry_X_Translation.svg"), 
                               labels = c("Size", 
                                          "Shape", 
                                          "90-Rot.", 
                                          "180-Rot.", 
                                          "X-Refl.", 
                                          "Y-Tran.",
                                          "X-Tran.",
                                          "Size", 
                                          "Shape", 
                                          "90-Rot.", 
                                          "180-Rot.", 
                                          "X-Refl.", 
                                          "Y-Tran.",
                                          "X-Tran."))


# add another column that codes the side of the y-symm transformation as a factor
tdata$Side <- factor(tdata$Ysym_side, levels = c("left", "right"), labels = c("left", "right"))



tdata$selection_rec <- factor(tdata$dv_selection_rec, levels = c("Ysym", "None", "not-Ysym"), labels = c("Y-Refl.", "None", "Not-Y-Refl."))
```

```{r}
table(tdata$condition)
table(tdata$Transformation)
```

# Graphs

```{r}
# create a summary dataset that also contains the percentages

plotdata_between <- tdata %>%
  group_by(Transformation, selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))



plotdata_sub <- subset(plotdata_between, selection_rec == "Y-Refl.")


```


```{r, echo = FALSE}

plotdata <- plotdata_between

# create a theme to handle the design 
myTheme <- theme(plot.title = element_text(face="bold", size = 16),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 20, angle = 45, hjust = 1), 
        axis.text.y = element_text(size = 18, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


theme_set(theme_light(base_size = 20, base_family = "Poppins"))


# append CI of the proportions 

plotdata_sub$n <- 30

plotdata_sub$SE <- sqrt((plotdata_sub$pct*(1-plotdata_sub$pct))/plotdata_sub$n)
plotdata_sub$CI <- 1.96 * plotdata_sub$SE



```






Get the CI values that will be plotted as error bars: 

see: https://rcompanion.org/handbook/H_02.html




```{r}
# create a summary dataset that also contains the percentages
plotdata_between <- tdata %>%
  group_by(Transformation, selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))


library(PropCIs)
library(DescTools)
library(purrr)

plotdata_between %>% 
  filter(Transformation == "Size") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> size_ci)
  

plotdata_between %>% 
  filter(Transformation == "Shape") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> shape_ci)


plotdata_between %>% 
  filter(Transformation == "90-Rot.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> ninerot_ci)


plotdata_between %>% 
  filter(Transformation == "180-Rot.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> huneightyrot_ci)


plotdata_between %>% 
  filter(Transformation == "X-Refl.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> xrefl_ci)
  

plotdata_between %>% 
  filter(Transformation == "Y-Tran.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> ytran_ci)


plotdata_between %>% 
  filter(Transformation == "X-Tran.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> xtran_ci)
  



ci_low <- c(size_ci[,2], shape_ci[,2], ninerot_ci[,2], huneightyrot_ci[,2], xrefl_ci[,2], ytran_ci[,2], xtran_ci[,2])

ci_up <- c(size_ci[,3], shape_ci[,3], ninerot_ci[,3], huneightyrot_ci[,3], xrefl_ci[,3], ytran_ci[,3], xtran_ci[,3])
```


```{r}
plotdata$ci_low <- ci_low
plotdata$ci_up <- ci_up
```




```{r}

library(scales)
theme_set(theme_light(base_size = 12, base_family = "Poppins"))

pvalues_x <- c(1:7)
pvalues <- c(rep("p < .001",6), "p = .057")

g<- ggplot(plotdata, 
       aes(x = Transformation,
           y = pct,
           fill = selection_rec)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  scale_y_continuous(limits = seq(0, 2),
                     breaks = seq(0, 1, .25),
                     expand = c(0,0),
                     label = percent) +
  coord_cartesian(xlim =c(1, 7), ylim = c(0, 1.1))+
  #coord_cartesian(clip = "off")+
  geom_text(aes(label = lbl), 
            size = 3.5,
            position = position_dodge(width = 1),
            vjust = -7) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(y = "Percentage", 
       fill = "Selected Object",
       x = "Type of Transformation")+
  geom_pointrange(ymin = ci_low, ymax = ci_up, position = position_dodge(width = 0.89), shape = 22, size = 0.3)+
  #annotate(geom = "hline",yintercept = 0.5, y = 0.5, color = "black", size = 1, linetype='dotted')+
  #annotate("pointrange", x = plotdata$Transformation, y = plotdata$pct, 
   #        ymin = plotdata$ci_low, 
    #       ymax = plotdata$ci_up, 
     #      colour = "black", size = 0.8, shape = 22, fill = Transformation, fatten = 1)+
  #annotate("text", x = pvalues_x, y = Inf, label = pvalues, size = 4, vjust = 1.8)+
  theme(legend.position = "top", axis.title = element_text(size = 15), axis.text = element_text(size = 13, color = "black"),
        legend.text = element_text(size = 13),legend.title = element_text(size = 13))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

g

#ggsave("selections_between.pdf",width=6,height=5)
ggsave("selections_dodged.svg",width=12,height=5)
ggsave("selections_dodged.pdf",width=12,height=5)
```

The method "sisongalz" is the default method. It is also the most recently developed method, and we'll go with it. We nonetheless may want to check whether other methods lead immensely different results. 


# Data from pilot study

The pilot study was mostly identical with the main study but tested fewer subjects. One difference from the main study was that the pilot study contained an additional "explanation" screen where subjects were asked to write short explanations of their choice. 

```{r}
tdata_p <- read_csv("tdata_pilot.csv")
```


```{r}
table(tdata_p$gender) #%>% sum()

#tdata_p$age <- as.numeric(tdata_p$age)

mean(tdata_p$age)
sd(tdata_p$age)
min(tdata_p$age)
max(tdata_p$age)
```


```{r}

# add a column that represents the transformations as a factor
tdata_p$Transformation <- factor(tdata_p$test_stimulus, 
                               levels = c("img/Left_Y_Symmetry_Big.svg",
                                          "img/Left_Y_Symmetry_Angle.svg",
                                          "img/Left_Y_Symmetry_X_Rotation.svg",
                                          "img/Left_Y_Symmetry_X_Rotation_180.svg",
                                          "img/Left_Y_Symmetry_X_Symmetry.svg",
                                          "img/Left_Y_Symmetry_Y_Translation.svg",
                                          "img/Left_Y_Symmetry_X_Translation.svg",
                                          "img/Right_Y_Symmetry_Big.svg",
                                          "img/Right_Y_Symmetry_Angle.svg",
                                          "img/Right_Y_Symmetry_X_Rotation.svg",
                                          "img/Right_Y_Symmetry_X_Rotation_180.svg",
                                          "img/Right_Y_Symmetry_X_Symmetry.svg",
                                          "img/Right_Y_Symmetry_Y_Translation.svg",
                                          "img/Right_Y_Symmetry_X_Translation.svg"), 
                               labels = c("Size", 
                                          "Shape", 
                                          "90-Rot.", 
                                          "180-Rot.", 
                                          "X-Refl.", 
                                          "Y-Tran.",
                                          "X-Tran.",
                                          "Size", 
                                          "Shape", 
                                          "90-Rot.", 
                                          "180-Rot.", 
                                          "X-Refl.", 
                                          "Y-Tran.",
                                          "X-Tran."))


# add another column that codes the side of the y-symm transformation as a factor
tdata_p$Side <- factor(tdata_p$Ysym_side, levels = c("left", "right"), labels = c("left", "right"))



tdata_p$selection_rec <- factor(tdata_p$dv_selection_rec, levels = c("Ysym", "None", "not-Ysym"), labels = c("Y-Refl.", "None", "Not-Y-Refl."))
```

```{r}
table(tdata_p$condition)
table(tdata_p$Transformation)
```



```{r}
# create a summary dataset that also contains the percentages

plotdata_between <- tdata_p %>%
  group_by(Transformation, selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))



plotdata_sub <- subset(plotdata_between, selection_rec == "Y-Refl.")


```


```{r, echo = FALSE}

plotdata <- plotdata_between

# create a theme to handle the design 
myTheme <- theme(plot.title = element_text(face="bold", size = 16),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 20, angle = 45, hjust = 1), 
        axis.text.y = element_text(size = 18, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


theme_set(theme_light(base_size = 20, base_family = "Poppins"))


# append CI of the proportions 

plotdata_sub$n <- 30

plotdata_sub$SE <- sqrt((plotdata_sub$pct*(1-plotdata_sub$pct))/plotdata_sub$n)
plotdata_sub$CI <- 1.96 * plotdata_sub$SE



```






Get the CI values that will be plotted as error bars: 

see: https://rcompanion.org/handbook/H_02.html




```{r}
# create a summary dataset that also contains the percentages
plotdata_between <- tdata_p %>%
  group_by(Transformation, selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))


library(PropCIs)
library(DescTools)
library(purrr)

plotdata_between %>% 
  filter(Transformation == "Size") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> size_ci)
  

plotdata_between %>% 
  filter(Transformation == "Shape") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> shape_ci)


plotdata_between %>% 
  filter(Transformation == "90-Rot.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> ninerot_ci)


plotdata_between %>% 
  filter(Transformation == "180-Rot.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> huneightyrot_ci)


plotdata_between %>% 
  filter(Transformation == "X-Refl.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> xrefl_ci)
  

plotdata_between %>% 
  filter(Transformation == "Y-Tran.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> ytran_ci)


plotdata_between %>% 
  filter(Transformation == "X-Tran.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> xtran_ci)
  



ci_low <- c(size_ci[,2], shape_ci[,2], ninerot_ci[,2], huneightyrot_ci[,2], xrefl_ci[,2], ytran_ci[,2], xtran_ci[,2])

ci_up <- c(size_ci[,3], shape_ci[,3], ninerot_ci[,3], huneightyrot_ci[,3], xrefl_ci[,3], ytran_ci[,3], xtran_ci[,3])
```


```{r}
plotdata$ci_low <- ci_low
plotdata$ci_up <- ci_up
```




```{r}

library(scales)
theme_set(theme_light(base_size = 12, base_family = "Poppins"))

pvalues_x <- c(1:7)
pvalues <- c(rep("p < .001",6), "p = .057")

g<- ggplot(plotdata, 
       aes(x = Transformation,
           y = pct,
           fill = selection_rec)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  scale_y_continuous(limits = seq(0, 2),
                     breaks = seq(0, 1, .25),
                     expand = c(0,0),
                     label = percent) +
  coord_cartesian(xlim =c(1, 7), ylim = c(0, 1.1))+
  #coord_cartesian(clip = "off")+
  geom_text(aes(label = lbl), 
            size = 3.5,
            position = position_dodge(width = 1),
            vjust = -7) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(y = "Percentage", 
       fill = "Selected Object",
       x = "Type of Transformation")+
  geom_pointrange(ymin = ci_low, ymax = ci_up, position = position_dodge(width = 0.89), shape = 22, size = 0.3)+
  #annotate(geom = "hline",yintercept = 0.5, y = 0.5, color = "black", size = 1, linetype='dotted')+
  #annotate("pointrange", x = plotdata$Transformation, y = plotdata$pct, 
   #        ymin = plotdata$ci_low, 
    #       ymax = plotdata$ci_up, 
     #      colour = "black", size = 0.8, shape = 22, fill = Transformation, fatten = 1)+
  #annotate("text", x = pvalues_x, y = Inf, label = pvalues, size = 4, vjust = 1.8)+
  theme(legend.position = "top", axis.title = element_text(size = 15), axis.text = element_text(size = 13, color = "black"),
        legend.text = element_text(size = 13),legend.title = element_text(size = 13))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

g

#ggsave("selections_between.pdf",width=6,height=5)
ggsave("pilot_selections_dodged.svg",width=12,height=5)
ggsave("pilot_selections_dodged.pdf",width=12,height=5)
```


# Aggregate Pilot and Main 

```{r}
tdata_p <- subset(tdata_p, select = -c(explanation) )
tdata_t <- rbind(tdata, tdata_p)


table(tdata_t$condition)
table(tdata_t$Transformation)

```



```{r}
# create a summary dataset that also contains the percentages

plotdata_between <- tdata_t %>%
  group_by(Transformation, selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))



plotdata_sub <- subset(plotdata_between, selection_rec == "Y-Refl.")


```


```{r, echo = FALSE}

plotdata <- plotdata_between

# create a theme to handle the design 
myTheme <- theme(plot.title = element_text(face="bold", size = 16),
        axis.title.x = element_text(face = "bold", size = 20),
        axis.title.y = element_text(face = "bold", size = 20),
        axis.text.x = element_text(size = 20, angle = 45, hjust = 1), 
        axis.text.y = element_text(size = 18, angle = 0),
        legend.text = element_text(size = 18),
        legend.title = element_text(face = "bold", size = 18),
        strip.text.x = element_text(size = 18),
        #panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line.x = element_line(colour = "black"), 
        axis.line.y = element_line(colour = "black"),
        axis.text = element_text(colour ="black"), 
        axis.ticks = element_line(colour ="black"))


theme_set(theme_light(base_size = 20, base_family = "Poppins"))


# append CI of the proportions 

plotdata_sub$n <- 30

plotdata_sub$SE <- sqrt((plotdata_sub$pct*(1-plotdata_sub$pct))/plotdata_sub$n)
plotdata_sub$CI <- 1.96 * plotdata_sub$SE



```






Get the CI values that will be plotted as error bars

see: https://rcompanion.org/handbook/H_02.html




```{r}
# create a summary dataset that also contains the percentages
plotdata_between <- tdata_t %>%
  group_by(Transformation, selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))


library(PropCIs)
library(DescTools)
library(purrr)

plotdata_between %>% 
  filter(Transformation == "Size") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> size_ci)
  

plotdata_between %>% 
  filter(Transformation == "Shape") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> shape_ci)


plotdata_between %>% 
  filter(Transformation == "90-Rot.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> ninerot_ci)


plotdata_between %>% 
  filter(Transformation == "180-Rot.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> huneightyrot_ci)


plotdata_between %>% 
  filter(Transformation == "X-Refl.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> xrefl_ci)
  

plotdata_between %>% 
  filter(Transformation == "Y-Tran.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> ytran_ci)


plotdata_between %>% 
  filter(Transformation == "X-Tran.") -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> xtran_ci)
  



ci_low <- c(size_ci[,2], shape_ci[,2], ninerot_ci[,2], huneightyrot_ci[,2], xrefl_ci[,2], ytran_ci[,2], xtran_ci[,2])

ci_up <- c(size_ci[,3], shape_ci[,3], ninerot_ci[,3], huneightyrot_ci[,3], xrefl_ci[,3], ytran_ci[,3], xtran_ci[,3])
```


```{r}
plotdata$ci_low <- ci_low
plotdata$ci_up <- ci_up
```




```{r}

library(scales)
theme_set(theme_light(base_size = 12, base_family = "Poppins"))

pvalues_x <- c(1:7)
pvalues <- c(rep("p < .001",6), "p = .057")

g<- ggplot(plotdata, 
       aes(x = Transformation,
           y = pct,
           fill = selection_rec)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  scale_y_continuous(limits = seq(0, 2),
                     breaks = seq(0, 1, .25),
                     expand = c(0,0),
                     label = percent) +
  coord_cartesian(xlim =c(1, 7), ylim = c(0, 1.1))+
  #coord_cartesian(clip = "off")+
  geom_text(aes(label = lbl), 
            size = 3.5,
            position = position_dodge(width = 1),
            vjust = -7) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(y = "Percentage", 
       fill = "Selected Object",
       x = "Type of Transformation")+
  geom_pointrange(ymin = ci_low, ymax = ci_up, position = position_dodge(width = 0.89), shape = 22, size = 0.3)+
  #annotate(geom = "hline",yintercept = 0.5, y = 0.5, color = "black", size = 1, linetype='dotted')+
  #annotate("pointrange", x = plotdata$Transformation, y = plotdata$pct, 
   #        ymin = plotdata$ci_low, 
    #       ymax = plotdata$ci_up, 
     #      colour = "black", size = 0.8, shape = 22, fill = Transformation, fatten = 1)+
  #annotate("text", x = pvalues_x, y = Inf, label = pvalues, size = 4, vjust = 1.8)+
  theme(legend.position = "top", axis.title = element_text(size = 15), axis.text = element_text(size = 13, color = "black"),
        legend.text = element_text(size = 13),legend.title = element_text(size = 13))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

g

#ggsave("selections_between.pdf",width=6,height=5)
ggsave("pilot_and_main_selections_dodged.svg",width=12,height=5)
ggsave("pilot_and_main_selections_dodged.pdf",width=12,height=5)
```

# Graph averaging over transformations 

## Main study 

```{r}
# create a summary dataset that also contains the percentages

plotdata_between <- tdata %>%
  group_by(selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

```


```{r}

library(PropCIs)
library(DescTools)
library(purrr)

plotdata_between -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> selection_ci)
  

ci_low <- c(selection_ci[,2])

ci_up <- c(selection_ci[,3])
```


```{r}
plotdata <- plotdata_between

plotdata$ci_low <- ci_low
plotdata$ci_up <- ci_up
```



```{r}

library(scales)
theme_set(theme_light(base_size = 12, base_family = "Poppins"))

pvalues_x <- c(1:7)
pvalues <- c(rep("p < .001",6), "p = .057")

g<- ggplot(plotdata, 
       aes(x = selection_rec,
           y = pct,
           fill = selection_rec)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  scale_y_continuous(limits = seq(0, 2),
                     breaks = seq(0, 1, .25),
                     expand = c(0,0),
                     label = percent) +
  #coord_cartesian(xlim =c(1, 7), ylim = c(0, 1.1))+
  #coord_cartesian(clip = "off")+
  geom_text(aes(label = lbl), 
            size = 3.5,
            position = position_dodge(width = 1),
            vjust = -7) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(y = "Percentage", 
       fill = "Selected Object",
       x = "Selected Object ")+
  geom_pointrange(ymin = ci_low, ymax = ci_up, position = position_dodge(width = 0.89), shape = 22, size = 0.3)+
  #annotate(geom = "hline",yintercept = 0.5, y = 0.5, color = "black", size = 1, linetype='dotted')+
  #annotate("pointrange", x = plotdata$Transformation, y = plotdata$pct, 
   #        ymin = plotdata$ci_low, 
    #       ymax = plotdata$ci_up, 
     #      colour = "black", size = 0.8, shape = 22, fill = Transformation, fatten = 1)+
  #annotate("text", x = pvalues_x, y = Inf, label = pvalues, size = 4, vjust = 1.8)+
  theme(legend.position = "none", axis.title = element_text(size = 15), axis.text = element_text(size = 13, color = "black"),
        legend.text = element_text(size = 13),legend.title = element_text(size = 13))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  ggtitle("Main Study (N = 420)")

g

#ggsave("selections_between.pdf",width=6,height=5)
ggsave("main_averaged_over_transformations.svg",width=5,height=5)
ggsave("main_averaged_over_transformations.pdf",width=5,height=5)
```

## Pilot study 

```{r}
# create a summary dataset that also contains the percentages

plotdata_between <- tdata_p %>%
  group_by(selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

```


```{r}

library(PropCIs)
library(DescTools)
library(purrr)

plotdata_between -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> selection_ci)
  

ci_low <- c(selection_ci[,2])

ci_up <- c(selection_ci[,3])
```


```{r}
plotdata <- plotdata_between

plotdata$ci_low <- ci_low
plotdata$ci_up <- ci_up
```



```{r}

library(scales)
theme_set(theme_light(base_size = 12, base_family = "Poppins"))

pvalues_x <- c(1:7)
pvalues <- c(rep("p < .001",6), "p = .057")

g<- ggplot(plotdata, 
       aes(x = selection_rec,
           y = pct,
           fill = selection_rec)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  scale_y_continuous(limits = seq(0, 2),
                     breaks = seq(0, 1, .25),
                     expand = c(0,0),
                     label = percent) +
  #coord_cartesian(xlim =c(1, 7), ylim = c(0, 1.1))+
  #coord_cartesian(clip = "off")+
  geom_text(aes(label = lbl), 
            size = 3.5,
            position = position_dodge(width = 1),
            vjust = -7) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(y = "Percentage", 
       fill = "Selected Object",
       x = "Selected Object ")+
  geom_pointrange(ymin = ci_low, ymax = ci_up, position = position_dodge(width = 0.89), shape = 22, size = 0.3)+
  #annotate(geom = "hline",yintercept = 0.5, y = 0.5, color = "black", size = 1, linetype='dotted')+
  #annotate("pointrange", x = plotdata$Transformation, y = plotdata$pct, 
   #        ymin = plotdata$ci_low, 
    #       ymax = plotdata$ci_up, 
     #      colour = "black", size = 0.8, shape = 22, fill = Transformation, fatten = 1)+
  #annotate("text", x = pvalues_x, y = Inf, label = pvalues, size = 4, vjust = 1.8)+
  theme(legend.position = "none", axis.title = element_text(size = 15), axis.text = element_text(size = 13, color = "black"),
        legend.text = element_text(size = 13),legend.title = element_text(size = 13))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  ggtitle("Pilot Study (N = 215)")

g

#ggsave("selections_between.pdf",width=6,height=5)
ggsave("pilot_averaged_over_transformations.svg",width=5,height=5)
ggsave("pilot_averaged_over_transformations.pdf",width=5,height=5)
```




## Pilot and Main together

```{r}
# create a summary dataset that also contains the percentages

plotdata_between <- tdata_t %>%
  group_by(selection_rec) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

```


```{r}

library(PropCIs)
library(DescTools)
library(purrr)

plotdata_between -> transf
  
(MultinomCI(transf$n,
           conf.level=0.95,
           method="sisonglaz") -> selection_ci)
  

ci_low <- c(selection_ci[,2])

ci_up <- c(selection_ci[,3])
```


```{r}
plotdata <- plotdata_between

plotdata$ci_low <- ci_low
plotdata$ci_up <- ci_up
```



```{r}

library(scales)
theme_set(theme_light(base_size = 12, base_family = "Poppins"))

pvalues_x <- c(1:7)
pvalues <- c(rep("p < .001",6), "p = .057")

g<- ggplot(plotdata, 
       aes(x = selection_rec,
           y = pct,
           fill = selection_rec)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  scale_y_continuous(limits = seq(0, 2),
                     breaks = seq(0, 1, .25),
                     expand = c(0,0),
                     label = percent) +
  #coord_cartesian(xlim =c(1, 7), ylim = c(0, 1.1))+
  #coord_cartesian(clip = "off")+
  geom_text(aes(label = lbl), 
            size = 3.5,
            position = position_dodge(width = 1),
            vjust = -7) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(y = "Percentage", 
       fill = "Selected Object",
       x = "Selected Object ")+
  geom_pointrange(ymin = ci_low, ymax = ci_up, position = position_dodge(width = 0.89), shape = 22, size = 0.3)+
  #annotate(geom = "hline",yintercept = 0.5, y = 0.5, color = "black", size = 1, linetype='dotted')+
  #annotate("pointrange", x = plotdata$Transformation, y = plotdata$pct, 
   #        ymin = plotdata$ci_low, 
    #       ymax = plotdata$ci_up, 
     #      colour = "black", size = 0.8, shape = 22, fill = Transformation, fatten = 1)+
  #annotate("text", x = pvalues_x, y = Inf, label = pvalues, size = 4, vjust = 1.8)+
  theme(legend.position = "none", axis.title = element_text(size = 15), axis.text = element_text(size = 13, color = "black"),
        legend.text = element_text(size = 13),legend.title = element_text(size = 13))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  ggtitle("Pilot and Main Study together (N = 635)")

g

#ggsave("selections_between.pdf",width=6,height=5)
ggsave("pilot_and_main_averaged_over_transformations.svg",width=5,height=5)
ggsave("pilot_and_main_averaged_over_transformations.pdf",width=5,height=5)
```
